---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covid19mx

<!-- badges: start -->
[![Build Status](https://travis-ci.org/pages-themes/cayman.svg?branch=master)](https://travis-ci.org/pages-themes/cayman)
[![Gem Version](https://badge.fury.io/rb/jekyll-theme-cayman.svg)](https://badge.fury.io/rb/jekyll-theme-cayman)
![GitHub all releases](https://img.shields.io/github/downloads/fdzul/denhotspots/total?style=social)
<!-- badges: end -->


**covid19mx is a package developed in the department of prevention and control of diseases transmitted by vector of the [Secretary of Health of Veracruz](https://www.ssaver.gob.mx/) and with colaboration of the federal level**

The goal of covid19mx is to provide the Mexican COVID-19 (SARS-COV2) pandemic data into R.

## **overview**

**covid19mx** . 

  - **`gihi()`** calculate gi and hi local spatial statistic.
  - **`bivariate_map()`** generate a bivariate map.
  - **`subset_den()`** is a function for subset de dengue dataset.
  - **`data_geocoden()`** this function creates an address vector and replaces incorrect text.
  - **`geocoden()`** this function geocodes the addresses of the sinave database using Geocoding API.
  - **`save_geocoden()`** This function generates the RData file where it contains the geocoded data and the sinave dataset.
  - **`point_to_polygons()`** this function counts how many events for spatial uni.

## Installation

You can install the released version of covid19mx from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("covid19mx")
```

### Development version

To get a bug fix, or use a feature from the development version, you can
install denhotspots from GitHub.

Mac
``` r
# install.packages("devtools")
devtools::install_github("fdzul/covid19mx")
``` 

Linux
``` r
# install.packages("remotes")
remotes::install_github("fdzul/covid19mx")
``` 
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
knitr::kable(head(covid19mx::covid19mx))
```



